### 2016-01-25 inputs/introduction.tex
intro-14:54

studies (GWAS) can not handle missing data and require complete datasets. 

@@

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes).\\

>>>>

studies (GWAS) can not handle missing data and require complete datasets (e.g. \cite{hayes2009invited}). 

@@

as high as 0.84-0.94 (measured as $R^{2}$ between true and imputed genotypes). Imputation of missing GBS data without alignment to the reference genome has been reported in alfalfa (``Medicago sativa'', \cite{Rocher_validation_2015}) and red raspberry (``Rubus idaeus'', \cite{ward2013}).\\
